
\section{Frameworks}
In this section, we will discuss the various frameworks and technologies that are being utilized in the project. This includes both the backend and frontend technologies, as well as any other tools that are essential for the development process.

\begin{list}{}
    \item \textbf{Programming language:} Go is used as the primary programming language for the backend services, leveraging its concurrency features and performance.
    \item \textbf{Logging:} Logrus is used for structured logging in the application, providing a simple API for logging that allows to pass the container ip address for each log entry to easily identify which node the log entry originated from.
    \item \textbf{Containerization:} Docker in swarm mode is used for container orchestration, enabling the management of multiple containers.
    \item \textbf{Automation:} A Makefile exsists to automate common tasks such as building and deploying the application, making it easier to manage the deployment and development process.
    \item \textbf{Testing:} The built-in testing package in Go is used for unit testing, ensuring that the code is reliable and functions as expected.
    \item \textbf{Command Line Interface:} The Cobra package is used to create a command line interface for the application, allowing users to interact with the application through the terminal.
    \item \textbf{Code Coverage:} Go tool cover is used to measure code coverage, ensuring that the code is adequately tested and that critical paths are covered by tests (see Makefile, coverage).
    \item \textbf{Continuous Integration:} GitHub Actions is used for continuous integration, automating the testing process.
    \item \textbf{Version Control:} Git and GitHub are used for version control, enabling collaboration and code management.
    \item \textbf{Project Management:} GitHub Projects is used for project management, providing a visual way to track progress and manage tasks.
    \item \textbf{Documentation:} LaTeX is used for documentation, providing a professional and structured way to present information.
\end{list}